Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-26 sections/eval.tex
fixes
Update on Overleaf.

@@

\willow{Note: I may want to explain format inference somewhere in here, but I'll have to get to it a little later, perhaps after the paper deadline}

>>>>

Sparse Matrix-Matrix Multiplication (SpGEMM) is a fundamental operation in scientific computing and data analytics. SpGEMM focuses on efficiently computing the product of two sparse matrices to produce an output sparse matrix. Inner product involves multiplying two matrices by taking dot products of corresponding rows and columns. Gustavson product optimizes memory access by storing one matrix in row-major order and the other in column-major order. Outer product computes the product of all pairs of elements from the input matrices. Our results indicate that inner and Gustavson products perform competitively, while outer product exhibits different characteristics, especially with sparse matrices.

@@

\willow{Note: I may want to explain format inference somewhere in here, but I'll
have to get to it a little later, perhaps after the paper deadline}
\willow{Note: I think it would be cool to include something about how we support
numerically stable norms and argmin in this model}
